\section{Plotted data}

I have chosen to look more in depth at run 7, 13 and 22.

\subsection{Fitness and entropy run 7}
\insertplot{blotto-2}{Fitness plot with B = 5, $R_f$ = 1.0 and $L_f$ = 0.4}
\insertplot{blotto-entropy-2}{Average entropy plot with B = 5, $R_f$ = 1.0 and $L_f$ = 0.4}

It is clear that with $R_f$ = 1.0 and $L_f$ = 0.4, the strategy is to focus the forces in one 
battle. As the avg entropy in \autoref{blotto-entropy-3} starts high, and gets reduced as generations go.
There was a climb in the entropy in the final 50 generations with this run. There was some competition 
around the generations 150-160. It might be that due to the $R_f$, after winning multiple battles
it tried to move some of the "redundant" forces from the first battle to win more battles.

\subsection{Fitness and entropy run 13}
\insertplot{blotto-3}{Fitness plot with B = 10, $R_f$ = 0.0 and $L_f$ = 1.0}
\insertplot{blotto-entropy-3}{Average entropy plot with B = 10, $R_f$ = 0.0 and $L_f$ = 1.0}

In this example we can clearly see the effects of high $L_f$. The $L_f$ will make it so that if
you lose the first battle, you will take a massive hit for the next battles. So the best strategy
was to move the forces to the first battle. As we can see from the avg entropy and fitness plot,
all the Colonels had to do the same. In the final generations the highest and average fitness
were equivelent. 

\subsection{Fitness and entropy run 22}
\insertplot{blotto-4}{Fitness plot with B = 20, $R_f$ = 0.3 and $L_f$ = 1.0}
\insertplot{blotto-entropy-4}{Average entropy plot with B = 20, $R_f$ = 0.3 and $L_f$ = 1.0}

There was a competition between two strong strategies. With the settings of $R_f$ and $L_f$, the
was to have the main focus on the first battle, but also distribute some of the forces out to the remanding
battles. \\

One strategy has 10\% more of the forces in the first battle. This had it's advantages, since the last 5-6 generations,
this strategy was the best. As the weaker strategy lost against the dominant in the first round, he took major hits
from the strength reduction.
